Running an open experiment: transparency and reproducibility in soil and ecosystem science

### 2016-02-04 manuscript_methods/Open_experiment.Rmd
Added September test run data and email
See issue #31
Added figure and caption

@@

This model not appropriate for everyone/thing!

@@

* Not appropriate for every kind of study
* Fear of "being scooped"
* Question of open from beginning or only after publication
* Privacy concerns

>>>>

VLB: Supplementary Information sections have become repositories of data and of non-core analyses. How does our open experiment replace (improve upon?) SI? Thoughts?

@@

We don't present this model as perfect. First, there are a number of "best practices" of scientific computing {Wilson, 2014 #4337} that we did not employ: for example, there was no unit testing to ensure module correctness, nor an automated build tool automating the workflow (i.e., the individual scripts all have to be run manually).

Nor is this examine appropriate, or applicable, to all scientific research, even just in the fields of soil, ecosystem, and global change science.

@@

* Fear of "being scooped"
* Question of open from beginning or only after publication
* Privacy concerns

**References**

**Figure 1.** The 'repository' containing all code and data of a recent soil incubation experiment. From top to bottom: raw data from a lab analyzer is uploaded; an initial script processes raw data into a standardized, summarized form; a second script looks for inconsistencies and outliers in the data; a third computes final data products, summaries, statistics, and figures; and a final one integrates these products to produce a submission-ready manuscript. (This schematic slightly simplifies the actual repository structure.) The repository is publicly available at https://github.com/bpbond/cpcrw_incubation, and throughout the experiment showed real-time updated diagnostics summarizing progress.

![Repository and workflow](figureX.png)
